Elephant Seal Age JAE Intraspecific Variation

### 2023-11-13 paper/paperv2.qmd
Changing the styling of phenology table

phenology_models %>% 
  select(-c(model_data, model)) %>% 
  pivot_longer(age_coef:breeder_signif, 
               names_to = c("param", "metric"),
               names_sep = "_",
               values_to = "value") %>% 
  pivot_wider(names_from = metric, values_from = value) %>% 
  mutate(coef = str_glue("{round(coef, 2)} +- {round(stderr, 2)}"),
         signif = str_glue("p = {round(pval, 4)} ({signif == 1})")) %>% 
  select(-c(stderr, pval)) %>% 
  pivot_wider(names_from = param, values_from = c(coef, signif)) %>% 
  select(phenology, ends_with("age"), ends_with("breeder")) %>% 
  knitr::kable()

>>>>

phenology_models %>% 
  select(-c(model_data, model)) %>% 
  pivot_longer(age_coef:breeder_signif, 
               names_to = c("param", "metric"),
               names_sep = "_",
               values_to = "value") %>% 
  pivot_wider(names_from = metric, values_from = value) %>% 
  mutate(coef = str_glue("{round(coef, 2)} +- {round(stderr, 2)}"),
         signif = str_glue("p = {round(pval, 4)} ({signif == 1})")) %>% 
  select(-c(stderr, pval)) %>% 
  pivot_wider(names_from = param, values_from = c(coef, signif)) %>% 
  select(phenology, ends_with("age"), ends_with("breeder")) %>% 
  knitr::kable(col.names = c("Phenology", 
                             "Age coef. (days/year)", 
                             "Significance", 
                             "Breeding status coef. (days)", 
                             "Significance")) %>% 
  kableExtra::kable_styling()
